Assessing glymphatic transport velocities by adjoint methods

### 2018-10-09 tex/paper.tex
text added

The observations $u_{obs}$ have fixed time-points $t_i$, these time-points may not correspond to the time discretization in the forward problem. Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation. If it did, then a linear interpolation of the current solution $u$ and previous solution $u_prev$ was used approximate the solution corresponding to $t_i$. The linear interpolation was given as  
\begin{equation}
u_{linear} = \frac{\Delta t}{dt} U_{prev} + \frac{dt - \Delta t }{dt} U,
\end{equation}
with $\Delta t$ is the difference between observation time and the time in the forward problem.

@@

@@

The difference in $S_0$ between observation times were adjusted for in \citep{ringstad2018brain}.  

@@

and we can then estimate concentration using Eq.\ref{EQ::contrast} if we know $T_{1}\sp{0}$. The $T_{1}\sp{0}$ values were obtained by T1 mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}. This makes it possible to also take into account patients specific characteristic, such as tissue damage. Tissue damage, such as edema, will cause the intensity in the MRI to differ from healthy white matter tissue. Indicating that the tissue composition in the edema is different, and subsequently have different T1 relaxation times, which will give a wrong estimation of the MRI contrast.

@@

Thus the optimized parameters will be compared with the apparent diffusion coefficient obtained form DTI cite DTI. The DTI measure the apparent diffusion coefficient 
Therefore the Stokes-Einstein relation [cite] can be used to estimate the apparent diffusion coefficient for whit and grey matter.

@@

\subsection{The relaxation parameters}
The relaxation parameters needs to be calibrated depending on the problem, and thus the diffusion parameters were computed by large range of relaxation parameters values. The results are shown in Tab.\ref{Tab::1}, and it is shown in red that $\alpha=1.0$ have large discrepancy in the parameters values of $D_{\Omega_1}$.

\subsection{The number of timessteps}
The first results focus on the accuracy of the minimization based on the number of time steps. It can be assumed that the error decreases  while the number of time steps increases since the Dirichlet boundary condition in Eq.\ref{EQ::DIRI} are quadratic, while the forward problem is a linear approximation.

This can be seen in Tab.??, Tab.??

@@

\subsection{The number of observations}
The number of observations can also be considered an important aspect, since the number of observations can be limited. Thus the number of observations set to $5,10 $ and $20$, and

The noise susceptibility can be seen in Tab. ?? and Tab. ??, and we see that a noise amplitude of $10 \%$ does not lead to significant change

@@

The diffusion equation does not pose any difficulties numerically

This method can be adapted to

@@

\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and estimated optimal parameters for the diffusion coefficients. }
\resizebox{0.9\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} = 1000$ & $ D_{\Omega_2} = 4.0 $ & $D_{\Omega_3} = 8.0 $ & $g$ \\
\hline
\rowcolor{red}  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\

 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
 1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
 1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
 1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\

 1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
 1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 184 	 & +0.005 & +0.065 & +0.039 & +0.039 \\ 
 1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 195 	 & +0.005 & +0.065 & +0.039 & +0.049 \\ 
 1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 205 	 & +0.005 & +0.065 & +0.039 & +0.050 \\

 1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
 1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
 1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
 1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
 1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
 1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
 1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\

 1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 152 	 & -0.006 & +0.062 & +0.039 & +0.022 \\ 
 1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 99 	 & -0.008 & +0.062 & +0.039 & +0.026 \\

 1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
 1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
 1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\

 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
 1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 134 	 & -0.008 & +0.062 & +0.039 & +0.023 \\ 
 1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
\end{tabular}}
\label{Tab::1}
\end{table}

\newpage
\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.03, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
\hline
 1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
 1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\

 1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\

 1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\

 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
 1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\

 1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
 1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
 1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\

>>>>

Each observations $u_{obs}$ have a fixed time-point $t_i$, these time-points may not overlap with the time discretization in the forward problem. Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation. If it did, then a linear interpolation of the current solution $u$ and previous solution $U_{prev}$ was used approximate the solution corresponding to $t_i$. The linear interpolation was given as  
\begin{equation}
u_{linear}(t) = \frac{\Delta t}{dt} U_{prev}(t) + \frac{dt - \Delta t }{dt} U(t), t \in \lbrace 
\end{equation}
with $\Delta t$ is the difference between observation time and the time in the forward problem.

@@

The

@@

The difference in $S_0$ between observation times were adjusted for in \cite{ringstad2018brain}.  

@@

and we can then estimate concentration using Eq.\ref{EQ::contrast} if we know $T_{1}\sp{0}$. The $T_{1}\sp{0}$ values were obtained by T1 mapping the brain using a MRI sequence known as MOLLI5(3)3 \cite{TAYLOR201667}. This makes it possible to  take into account patients specific characteristic, such as tissue damage. There are several forms of tissue damage, one is edema, which can be observed in the MRI due to a lower intensity in the white matter compared to healthy white matter tissue. This means that the damaged tissue also have different T1 relaxation times, which will give wrong estimation of tracer concentration.

@@

Thus the optimized parameters will be compared with the apparent diffusion coefficient obtained form DTI cite DTI. The DTI measure the apparent diffusion coefficient

The Stokes-Einstein relation combined with correlation between weight and radius of particles can be used to estimate the diffusion coefficient for Gadovist (600 Da) \cite{VALENCIA2011129}. This gives a estimated free diffusion coefficient of 
$  25.72 e-5 \mathrm{mm\sp{2}/s}$.

@@

The relative error norm for a scalar is defined as 
\begin{equation}
|| X ||_{RE} = \frac{X_{found} -X_{true} }{ X_true }
\end{equation}
with $X$ as an arbitrary scalar parameter.

The relative error norm for the boundary is defined as 
\begin{equation}
|| g ||_{RE(\Omega_1)} = \frac{||g_{found} -g_{true}||_{L(\Omega_1)} }{ ||g_{true}|| }
\end{equation}
with $X$ as a vector.
\subsection{The relaxation parameters}

The robustness of the objective functional defined in Eq.\ref{Eq::F} is dependent on the regularization parameters $\alpha$ and $\beta$. Therefore it is important to select regularization parameter values to ensure effective and accurate convergence. The evaluation of different regularization parameters was done by solving the optimization  with  different values of $\alpha$ and $\beta$ and compare the resulting states and the manufactured solution. The observation times were selected with $t_i \in  \rbrace 2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0 \lbrace$, and the number of time-steps in the forward problem was set to $k= 10$.

The results are shown in Tab.\ref{Tab::1} together with the number of iteration used to reach the convergence criteria. It can be observed for $\alpha= 1.0$ that there is a significant relative error for $D_{\Omega_1}$.  The other control parameters also showed an increased error compared to other values of $\alpha$. The remaining values of the regularization parameters give small relative error.

The MRI data contains noise, hence an investigation to the noise susceptibility is needed. This is done by adding uniform noise in the range $\brace -n_{amp} , n_{amp} \rbrace $, with $n_{amp}$ defined as noise amplitude, to the manufactured observations. Then the optimization was solved by varying the regularization parameters $\alpha$ and $\beta$.

In Tab.\ref{Tab::Noise0.03}, we can see that a noise amplitude of 0.03, (10$\%$ of maximum initial condition) had negligible effect on the relative error. However, in Tab.\ref{Tab::Noise0.3} the noise amplitude was increased to 0.3 (100$\%$ of maximum initial condition) and it is observed that for  $\alpha < 1.0e-3$  $\beta < 1.0e-3$ the optimization failed to converge before reaching maximum iteration of 1000 steps. Furthermore, the relative boundary error $||g||_{RE(\Omega)}$ is  larger for lower values of $\beta$.

\subsection{The number of timessteps}

The PDE uses backward Euler, which is a linear approximation in time. This means that the increasing the number of timesteps will allow for a better temporal approximation, but will also increase the computational cost. Thus finding the best number of timesteps can be beneficial.

@@

\subsection{The number of observations}

The dependency on observations is relevant, since the number of observations of MRI data is limited. This was investigated by changing the number of observations, and examine the resulting states. The number of observation were chosen to be 5, 10  and 20, and times were set to be evenly spaced.

The results are shown in Tab.??, Tab.\ref{TAB::double} and Tab.\ref{TAB::half}. 
\subsection{Sparse observations}

The MRI data contains observations after the injection of CSF tracer. These observation are unevenly distributed in time, and thus there are large time intervals with no observations. Thus the effect of this temporal gap in the observations will be evaluated. This is done by selecting the observation times as follows  $t_i = [0.8, 1.0, 1.2, 1.8, 2.4, 3.6, 5.4, 7.6, 24.0]$. Furthermore, the optimal regularization parameters and noise susceptibility was also checked.

\subsection{MRI Data}

The MRI data consisted of the observations at times $t_i \in \lbrace 0.00, 0.16, 0.39, 0.55, 0.77, 2.09, 6.05, 24.06, 47.84, 698.02 \rbrace (hours)$ and $t_i=0.00$ was the observation 1-2 hours after the tracer was injected. There was no signifcant visible change in the tracer between the observations at $\lbrace 0.16, 0.39, 0.55, 0.77 \rbrace$. This prompted the focus on the observation times  $0.00 2.09, 6.05, 24.06, 47.84$, which can be seen in Fig.??.

The time range for the selected observations

@@

@@

\begin{table}
\centering
\caption{Shows the regularization parameters $\alpha$ and $\beta$, number of timesteps $k$ and number of observation $\tau$ with the resulting number of iterations and the relative error for the control parameters. }
\resizebox{0.9\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ ||D_{\Omega_1}||$ & $ ||D_{\Omega_2}|| $ & $||D_{\Omega_3}||$ & $||g||$ \\
\hline
\rowcolor{red}  1.0e+00 	 & 1.0e+00 	 & 10 & 225 	 & +4.148 & +0.304 & +0.092 & +0.135 \\ 
%\rowcolor{red}  1.0e+00 	 & 1.0e-01 	 & 10 & 206 	 & +4.272 & +0.305 & +0.091 & +0.142 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-02 	 & 10 & 233 	 & +4.272 & +0.305 & +0.091 & +0.143 \\ 
%\rowcolor{red}  1.0e+00 	 & 1.0e-03 	 & 10 & 208 	 & +4.437 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-04 	 & 10 & 204 	 & +4.271 & +0.306 & +0.091 & +0.143 \\ 
%\rowcolor{red}  1.0e+00 	 & 1.0e-05 	 & 10 & 203 	 & +4.400 & +0.305 & +0.091 & +0.143 \\ 
\rowcolor{red}  1.0e+00 	 & 1.0e-06 	 & 10 & 222 	 & +4.584 & +0.304 & +0.090 & +0.143 \\

 1.0e-01 	 & 1.0e+00 	 & 10 & 207 	 & +0.127 & +0.093 & +0.041 & +0.027 \\ 
 %1.0e-01 	 & 1.0e-01 	 & 10 & 196 	 & +0.121 & +0.093 & +0.041 & +0.046 \\ 
 1.0e-01 	 & 1.0e-02 	 & 10 & 232 	 & +0.123 & +0.093 & +0.041 & +0.056 \\ 
 %1.0e-01 	 & 1.0e-03 	 & 10 & 183 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
 1.0e-01 	 & 1.0e-04 	 & 10 & 212 	 & +0.122 & +0.093 & +0.040 & +0.057 \\ 
 %1.0e-01 	 & 1.0e-05 	 & 10 & 168 	 & +0.122 & +0.093 & +0.041 & +0.057 \\
 1.0e-01 	 & 1.0e-06 	 & 10 & 195 	 & +0.122 & +0.093 & +0.041 & +0.057 \\

 1.0e-02 	 & 1.0e+00 	 & 10 & 227 	 & +0.015 & +0.067 & +0.039 & +0.018 \\ 
 %1.0e-02 	 & 1.0e-01 	 & 10 & 153 	 & +0.006 & +0.065 & +0.039 & +0.021 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 184 	 & +0.005 & +0.065 & +0.039 & +0.039 \\ 
 %1.0e-02 	 & 1.0e-03 	 & 10 & 176 	 & +0.004 & +0.065 & +0.039 & +0.048 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 195 	 & +0.005 & +0.065 & +0.039 & +0.049 \\ 
 %1.0e-02 	 & 1.0e-05 	 & 10 & 215 	 & +0.004 & +0.065 & +0.039 & +0.051 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 205 	 & +0.005 & +0.065 & +0.039 & +0.050 \\

 1.0e-03 	 & 1.0e+00 	 & 10 & 179 	 & +0.004 & +0.064 & +0.039 & +0.019 \\ 
 %1.0e-03 	 & 1.0e-01 	 & 10 & 221 	 & -0.005 & +0.063 & +0.039 & +0.018 \\ 
 1.0e-03 	 & 1.0e-02 	 & 10 & 89 	 & -0.007 & +0.063 & +0.039 & +0.026 \\ 
 %1.0e-03 	 & 1.0e-03 	 & 10 & 77 	 & -0.005 & +0.062 & +0.039 & +0.027 \\ 
 1.0e-03 	 & 1.0e-04 	 & 10 & 100 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
 %1.0e-03 	 & 1.0e-05 	 & 10 & 105 	 & -0.006 & +0.062 & +0.039 & +0.027 \\ 
 1.0e-03 	 & 1.0e-06 	 & 10 & 123 	 & -0.007 & +0.062 & +0.039 & +0.028 \\

 1.0e-04 	 & 1.0e+00 	 & 10 & 236 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
 %1.0e-04 	 & 1.0e-01 	 & 10 & 195 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 152 	 & -0.006 & +0.062 & +0.039 & +0.022 \\ 
 %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 106 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 %1.0e-04 	 & 1.0e-05 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 99 	 & -0.008 & +0.062 & +0.039 & +0.026 \\

 1.0e-05 	 & 1.0e+00 	 & 10 & 139 	 & +0.004 & +0.063 & +0.039 & +0.019 \\ 
 %1.0e-05 	 & 1.0e-01 	 & 10 & 170 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
 1.0e-05 	 & 1.0e-02 	 & 10 & 182 	 & -0.007 & +0.062 & +0.039 & +0.020 \\ 
 %1.0e-05 	 & 1.0e-03 	 & 10 & 70 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-05 	 & 1.0e-04 	 & 10 & 77 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 %1.0e-05 	 & 1.0e-05 	 & 10 & 104 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-05 	 & 1.0e-06 	 & 10 & 92 	 & -0.007 & +0.062 & +0.039 & +0.026 \\

 1.0e-06 	 & 1.0e+00 	 & 10 & 163 	 & +0.003 & +0.064 & +0.039 & +0.019 \\ 
 %1.0e-06 	 & 1.0e-01 	 & 10 & 218 	 & -0.006 & +0.062 & +0.039 & +0.018 \\ 
 1.0e-06 	 & 1.0e-02 	 & 10 & 134 	 & -0.008 & +0.062 & +0.039 & +0.023 \\ 
 %1.0e-06 	 & 1.0e-03 	 & 10 & 79 	 & -0.006 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-06 	 & 1.0e-04 	 & 10 & 107 	 & -0.007 & +0.062 & +0.039 & +0.026 \\ 
 %1.0e-06 	 & 1.0e-05 	 & 10 & 103 	 & -0.008 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-06 	 & 1.0e-06 	 & 10 & 91 	 & -0.008 & +0.062 & +0.039 & +0.026 \\  
\end{tabular}}
\label{Tab::1}
\end{table}

\newpage
\begin{table}
\centering
\caption{Shows the relaxation parameters $\alpha$ and $\beta$, number of timesteps $k$, the resulting number of iterations, the relative error of the estimated optimal parameters for the diffusion coefficients and the relative error for $g$. The noise amplitude was set to 0.03, and $\tau =[2.4, 4.8, 7.2, 9.6, 12.0, 14.4, 16.8, 19.2, 21.6, 24.0]$ }
\resizebox{0.8\textwidth}{!}{\begin{tabular}{*{8}c}
$\alpha$ & $\beta$ & k  & iter & $ D_{\Omega_1} $ & $ D_{\Omega_2} $ & $D_{\Omega_3} $ & wrong $g$ \\
\hline
 1.0e+00 	 & 1.0e+00 	 & 10 & 218 	 & +4.266 & +0.304 & +0.092 & +0.135 \\ 
 %1.0e+00 	 & 1.0e-01 	 & 10 & 223 	 & +4.565 & +0.304 & +0.090 & +0.142 \\ 
 1.0e+00 	 & 1.0e-02 	 & 10 & 199 	 & +4.268 & +0.305 & +0.090 & +0.143 \\ 
% 1.0e+00 	 & 1.0e-03 	 & 10 & 222 	 & +4.274 & +0.305 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-04 	 & 10 & 211 	 & +4.448 & +0.306 & +0.090 & +0.143 \\ 
% 1.0e+00 	 & 1.0e-05 	 & 10 & 227 	 & +4.527 & +0.304 & +0.090 & +0.143 \\ 
 1.0e+00 	 & 1.0e-06 	 & 10 & 263 	 & +4.266 & +0.306 & +0.091 & +0.143 \\

 1.0e-01 	 & 1.0e+00 	 & 10 & 167 	 & +0.131 & +0.093 & +0.041 & +0.027 \\ 
% 1.0e-01 	 & 1.0e-01 	 & 10 & 195 	 & +0.125 & +0.093 & +0.039 & +0.046 \\ 
 1.0e-01 	 & 1.0e-02 	 & 10 & 218 	 & +0.126 & +0.093 & +0.040 & +0.056 \\ 
% 1.0e-01 	 & 1.0e-03 	 & 10 & 161 	 & +0.129 & +0.094 & +0.040 & +0.057 \\ 
 1.0e-01 	 & 1.0e-04 	 & 10 & 180 	 & +0.135 & +0.092 & +0.042 & +0.057 \\ 
% 1.0e-01 	 & 1.0e-05 	 & 10 & 169 	 & +0.123 & +0.093 & +0.041 & +0.057 \\ 
 1.0e-01 	 & 1.0e-06 	 & 10 & 201 	 & +0.119 & +0.093 & +0.040 & +0.057 \\

 1.0e-02 	 & 1.0e+00 	 & 10 & 183 	 & +0.013 & +0.067 & +0.040 & +0.018 \\ 
% 1.0e-02 	 & 1.0e-01 	 & 10 & 149 	 & +0.002 & +0.066 & +0.038 & +0.021 \\ 
 1.0e-02 	 & 1.0e-02 	 & 10 & 185 	 & -0.005 & +0.065 & +0.040 & +0.040 \\ 
% 1.0e-02 	 & 1.0e-03 	 & 10 & 213 	 & +0.004 & +0.066 & +0.038 & +0.049 \\ 
 1.0e-02 	 & 1.0e-04 	 & 10 & 151 	 & +0.008 & +0.066 & +0.039 & +0.047 \\ 
% 1.0e-02 	 & 1.0e-05 	 & 10 & 197 	 & +0.004 & +0.064 & +0.040 & +0.051 \\ 
 1.0e-02 	 & 1.0e-06 	 & 10 & 185 	 & +0.012 & +0.063 & +0.038 & +0.049 \\

 1.0e-03 	 & 1.0e+00 	 & 10 & 183 	 & +0.007 & +0.062 & +0.038 & +0.019 \\ 
%1.0e-03 	 & 1.0e-01 	 & 10 & 181 	 & -0.011 & +0.063 & +0.039 & +0.019 \\ 
 1.0e-03 	 & 1.0e-02 	 & 10 & 122 	 & -0.008 & +0.063 & +0.040 & +0.025 \\ 
% 1.0e-03 	 & 1.0e-03 	 & 10 & 158 	 & -0.004 & +0.062 & +0.040 & +0.028 \\ 
 1.0e-03 	 & 1.0e-04 	 & 10 & 168 	 & -0.013 & +0.063 & +0.038 & +0.029 \\ 
% 1.0e-03 	 & 1.0e-05 	 & 10 & 120 	 & -0.010 & +0.063 & +0.040 & +0.028 \\ 
 1.0e-03 	 & 1.0e-06 	 & 10 & 132 	 & -0.002 & +0.062 & +0.039 & +0.028 \\

 1.0e-04 	 & 1.0e+00 	 & 10 & 176 	 & +0.000 & +0.063 & +0.039 & +0.019 \\ 
 %1.0e-04 	 & 1.0e-01 	 & 10 & 180 	 & -0.001 & +0.062 & +0.039 & +0.019 \\ 
 1.0e-04 	 & 1.0e-02 	 & 10 & 120 	 & +0.000 & +0.063 & +0.039 & +0.024 \\ 
 %1.0e-04 	 & 1.0e-03 	 & 10 & 119 	 & -0.004 & +0.062 & +0.039 & +0.026 \\ 
 1.0e-04 	 & 1.0e-04 	 & 10 & 77 	 & -0.005 & +0.061 & +0.038 & +0.027 \\ 
 %1.0e-04 	 & 1.0e-05 	 & 10 & 104 	 & -0.004 & +0.062 & +0.038 & +0.027 \\ 
 1.0e-04 	 & 1.0e-06 	 & 10 & 109 	 & -0.007 & +0.062 & +0.039 & +0.027 \\

 1.0e-05 	 & 1.0e+00 	 & 10 & 220 	 & +0.005 & +0.063 & +0.039 & +0.019 \\ 
 %1.0e-05 	 & 1.0e-01 	 & 10 & 193 	 & -0.009 & +0.062 & +0.039 & +0.019 \\ 
 1.0e-05 	 & 1.0e-02 	 & 10 & 163 	 & -0.013 & +0.063 & +0.039 & +0.021 \\ 
 %1.0e-05 	 & 1.0e-03 	 & 10 & 115 	 & -0.007 & +0.063 & +0.040 & +0.026 \\ 
 1.0e-05 	 & 1.0e-04 	 & 10 & 82 	 & -0.007 & +0.062 & +0.038 & +0.027 \\ 
 %1.0e-05 	 & 1.0e-05 	 & 10 & 145 	 & -0.001 & +0.062 & +0.039 & +0.027 \\ 
 1.0e-05 	 & 1.0e-06 	 & 10 & 147 	 & -0.012 & +0.061 & +0.040 & +0.027 \\
